```{r knitsetup, echo = FALSE, results = 'hide', warning = FALSE, message = FALSE, cache = FALSE}
opts_knit$set(base.dir = './', fig.path = '', out.format = 'md')
opts_chunk$set(prompt = TRUE, comment = '', results = 'markup', fig.path = '../Figure/')
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here
# end setup chunk
```
# knitcitations: Citations for knitr markdown files

RMarkdownでの文献管理

[![](http://www.r-pkg.org/badges/version/knitcitations)](http://cran.rstudio.com/web/packages/knitcitations/index.html)

* CRAN: http://cran.r-project.org/web/packages/knitcitations/index.html
* GitHub: https://github.com/cboettig/knitcitations

```{r}
library(knitcitations)
```

バージョン: `r packageVersion("knitcitations")`

-----

```{r, echo = FALSE, results = "asis", eval = FALSE}
library(help = "knitcitations")$info[[2]] %>% data.frame() %>% kable()
```

| 関数名 | 概略 |
|--------|------|
| `bib_metadata` | get the full metadata for a citation / bibliographic object |
| `bibliography` | Generate the bibliography |
| `cite_options` | Toggles for various citation options   |
| `citep` | citep - inline parenthetical citation |
| `citet` | citet - inline parenthetical citation  |
| `cleanbib` | cleanbib |
| `greycite` | greycite citation method |
| `read.bibtex` | read.bibtex |
| `record_as_cited` | record as cited |
| `write.bibtex` | write a bibtex file |
