```{r knitsetup, echo = FALSE, results = 'hide', warning = FALSE, message = FALSE, cache = FALSE}
opts_knit$set(base.dir = './', fig.path = '', out.format = 'md')
opts_chunk$set(prompt = TRUE, comment = '', results = 'markup', fig.path = '../Figure/')
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here
# end setup chunk
```
# xtable: Export tables to LaTeX or HTML

表形式のデータをLaTeXやHTMLとして出力

[![](http://www.r-pkg.org/badges/version/xtable)](http://cran.rstudio.com/web/packages/xtable/index.html)

* CRAN: http://cran.r-project.org/web/packages/xtable/index.html
* URL: http://xtable.r-forge.r-project.org/

```{r}
library(xtable)
```

バージョン: `r packageVersion("xtable")`

-----

```{r, echo = FALSE, results = "asis", eval = FALSE}
library(help = "xtable")$info[[2]] %>% data.frame() %>% kable()
```

| 関数名 | 概略 |
|--------|------|
| `caption` | Retrieve and Set Options for Export Tables |
| `print.xtable` | Print Export Tables |
| `string` | String handling functions |
| `tli` | Math scores from Texas Assessment of Academic Skills (TAAS) |
| `toLatex.xtable` | Convert Table to Latex |
| `xtable` | Create Export Tables |
