```{r knitsetup, echo = FALSE, results = 'hide', warning = FALSE, message = FALSE, cache = FALSE}
opts_knit$set(base.dir = './', fig.path = '', out.format = 'md')
opts_chunk$set(prompt = TRUE, comment = '', results = 'markup', fig.path = '../Figure/')
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here
# end setup chunk
```
# magrittr: A Forward-Pipe Operator for R

Rにパイプ演算子を導入する

[![](http://www.r-pkg.org/badges/version/magrittr)](http://cran.rstudio.com/web/packages/magrittr/index.html)

* CRAN: http://cran.r-project.org/web/packages/magrittr/index.html
* GitHub: https://github.com/smbache/magrittr

```{r}
library(magrittr)
```

バージョン: `r packageVersion("magrittr")`

-----

```{r, echo = FALSE, results = "asis", eval = FALSE}
library(help = "magrittr")$info[[2]] %>% data.frame() %>% kable()
```

| 関数名 | 概略 |
|--------|------|
| `%$%` | magrittr exposition pipe-operator |
| `%<>%` | magrittr compound assignment pipe-operator |
| `%>%` | magrittr forward-pipe operator |
| `%T>%` | magrittr tee operator |
| `[[.fseq` | Extract function(s) from a functional sequence. |
| `debug_fseq` | Debugging function for functional sequences. |
| `debug_pipe` | Debugging function for magrittr pipelines. |
| `extract` | Aliases |
| `freduce` | Apply a list of functions sequentially |
| `functions` | Extract the function list from a functional sequence. |
| `magrittr` | magrittr - Ceci n'est pas un pipe |
| `print.fseq` | Print method for functional sequence. |
