```{r knitsetup, echo = FALSE, results = 'hide', warning = FALSE, message = FALSE, cache = FALSE}
opts_knit$set(base.dir = './', fig.path = '', out.format = 'md')
opts_chunk$set(prompt = TRUE, comment = '', results = 'markup', fig.path = '../Figure/')
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here
# end setup chunk
```
# Nippon: Japanese utility functions and data

日本語ユーザーのための便利な関数とデータセット

[![](http://www.r-pkg.org/badges/version/Nippon)](http://cran.rstudio.com/web/packages/Nippon/index.html)

* CRAN: http://cran.r-project.org/web/packages/Nippon/index.html

```{r}
library(Nippon)
```

バージョン: `r packageVersion("Nippon")`

-----

```{r, echo = FALSE, results = "asis", eval = FALSE}
library(help = "Nippon")$info[[2]] %>% data.frame() %>% kable()
```

| 関数名 | 概略 |
|--------|------|
| `JapanPrefecturesMap` | A simple choropleth map of Japan |
| `JapaneseColors` | Find RGB by Japanese color names |
| `Nippon-internal` | Internal objects in the Nippon package |
| `Nippon-package` | Japanese utility functions and data |
| `jholiday` | Calculate public holidays in Japan |
| `jyear` | Conversion to Japanese year style |
| `kakasi` | Interface to kakasi |
| `kana2roma` | Romanization of Japanese |
| `kata2hira` | Conversion form Katakana to Hiragana |
| `month.name.jp` | The Japanese name of months |
| `nippon.palette` | Switch the color palette to JIS colors |
| `prefectures` | Prefectural names in Japan |
| `sjis2utf8` | Wrapper of iconv for Japanese encoding |
| `zen2han` | Convert Japanese characters from fullwidth (zenkaku) to halfwidth (hankaku) forms |

## sjis2utf8

```{r usage_sjis2utf8}
iconv(zenkaku$upper, from = "UTF-8", to = "CP932") %>% sjis2utf8()
```

## kata2hira

片仮名と平仮名の相互変換

```{r usage_kata2hira}
katakana()[26:30]
kata2hira(katakana()[26:30])

hiragana()[21:25]
hira2kata(hiragana()[21:25])
```

## zen2han

全角英数字を半角英数字に変換する

```{r usage_zen2han}
c("０", "Ｆ") %>% zen2han()
```
