```{r knitsetup, echo = FALSE, results = 'hide', warning = FALSE, message = FALSE, cache = FALSE}
opts_knit$set(base.dir = './', fig.path = '', out.format = 'md')
opts_chunk$set(prompt = TRUE, comment = '', results = 'markup', fig.path = '../Figure/')
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here
# end setup chunk
```
# readr: Read Tabular Data

表形式のデータを読み込むためのパッケージ

[![](http://www.r-pkg.org/badges/version/readr)](http://cran.rstudio.com/web/packages/readr/index.html)

* CRAN: http://cran.r-project.org/web/packages/readr/index.html
* GitHub: http://github.com/hadley/readr

```{r}
library(readr)
```

バージョン: `r packageVersion("readr")`

-----

```{r, echo = FALSE, results = "asis", eval = FALSE}
library(help = "readr")$info[[2]] %>% data.frame() %>% kable()
```

| 関数名 | 概略 |
|--------|------|
| `collector` | Parse character vectors into typed columns.   |
| `count_fields` | Count the number of fields in each line of a file. |
| `parse_datetime` | Parse a character vector of dates or date times. |
| `problems` | Retrieve parsing problems. |
| `read_delim` | Read a delimited file into a data frame. |
| `read_file` | Read a file into a string. |
| `read_fwf` | Read a fixed width file. |
| `read_lines` | Read lines from a file or string. |
| `read_log` | Read common/combined log file. |
| `read_table` | Read text file where columns are separated by whitespace. |
| `type_convert` | Re-convert character columns in existing data frame. |
| `write_csv` | Save a data frame to a csv file. |

## read_delim

カンマ区切りのファイル（`.csv`）を読み込む

```{r, eval = FALSE}
read_csv(file, col_names = TRUE, col_types = NULL, na = "NA", skip = 0, n_max = -1, progress = interactive())
```

> 日付データなどは形式を指定して読み込むことが可能（？）

### 参考

* [R の read.csv() と read.csv2() の違い #rstatsj - Qiita](http://qiita.com/hoxo_m/items/959d141cf7297e2e80d3)
