```{r knitsetup, echo = FALSE, results = 'hide', warning = FALSE, message = FALSE, cache = FALSE}
opts_knit$set(base.dir = './', fig.path = '', out.format = 'md')
opts_chunk$set(prompt = TRUE, comment = '', results = 'markup', fig.path = '../Figure/')
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here
# end setup chunk
```
# tidyr: Easily Tidy Data with spread() and gather() Functions

データ解析を容易にするデータ整形のためのパッケージ

[![](http://www.r-pkg.org/badges/version/tidyr)](http://cran.rstudio.com/web/packages/tidyr/index.html)

* CRAN: http://cran.r-project.org/web/packages/tidyr/index.html
* GitHub: http://github.com/hadley/tidyr

```{r}
library(tidyr)
```

バージョン: `r packageVersion("tidyr")`

-----

```{r, echo = FALSE, results = "asis", eval = FALSE}
library(help = "tidyr")$info[[2]] %>% data.frame() %>% kable()
```

| 関数名 | 概略 |
|--------|------|
| `expand` | Expand data frame to include all combinations of levels. |
| `extract` | Extract one column into multiple columns. |
| `extract_numeric` | Extract numeric component of variable. |
| `gather` | Gather columns into key-value pairs. |
| `separate` | Separate one column into multiple columns. |
| `seq_range` | Create an evenly spaced sequence of values from highest to lowest. |
| `spread` | Spread a key-value pair across multiple columns. |
| `spread_` | Standard-evaluation version of 'spread'. |
| `unite` | Unite multiple columns into one. |
| `unnest` | Unnest a list column. |
| `unnest_` | Standard-evaluation version of 'unnest'. |

## extract

１つの行を複数の行に分割する

## extract_numeric

データから数値だけを抜き出す

## gather

複数の変数に分かれている**共通の変数**を１つの変数としてまとめる
